Données de vaccination et Etude socioéconomique

### 2021-10-18 code/manhattan_animated.Rmd
update RMD

@@

<!-- === -->
```{r, eval = F, echo = F}
vacc_com = read_csv2(url(paste0("https://datavaccin-covid.ameli.fr/explore/dataset/donnees-de-vaccination-par-commune/download/?format=csv&refine.classe_age=", "00-19", "&refine.semaine_injection=2021-", "35", "&timezone=Europe/Berlin&lang=fr&use_labels_for_header=true&csv_separator=%3B"))) %>%
  mutate(codgeo = as.numeric(commune_residence)) %>%
  mutate(taux_cumu_1_inj = as.numeric(taux_cumu_1_inj))

vacc = read_csv2(url(paste0("https://datavaccin-covid.ameli.fr/explore/dataset/donnees-de-vaccination-par-epci/download/?format=csv&refine.semaine_injection=2021-", "35", "&refine.classe_age=", "00-19", "&timezone=Europe/Berlin&lang=fr&use_labels_for_header=true&csv_separator=%3B"))) %>%
  mutate(codgeo = as.numeric(epci)) %>%
  mutate(taux_cumu_1_inj = as.numeric(taux_cumu_1_inj)) %>%
  plyr::rbind.fill(vacc_com)

@@

questionr::odds.ratio(factor(test$Overcrowding_rate, levels = c(0,1), labels = c(0,1)), test$taux_cumu_1_inj)
```

@@

plot_ly(
  fig,
  x = ~pos,
  y = ~`max_OR-inv_OR`,
  size = ~-log10(p),
  color = ~theme,
  frame = ~week,
  text = ~Variable,
  alpha = 0.75,
  symbol = ~shape,
  symbols = c(220, 219),
  hooverinfo = "text",
  type = "scatter",
  mode = "markers"
  # error_y = list(array = ~inf,
  #                arrayminus = ~sup,
  #                symmetric = FALSE,
  #                type = "data")
) %>%
  layout(
    xaxis = list(title = "Variable"),
    yaxis = list(title = "max(OR, 1/OR)"))

@@

>>>>

fig = data %>%
  mutate(shape = if_else(OR > 1, 219, 220)) %>%
  mutate(inf = if_else(OR > 1, `2.5 %`, `inv_2.5 %`),
         sup = if_else(OR > 1, `97.5 %`, `inv_97.5 %`),
         value = (sup-inf))
# filter(week == 33) %>%
# arrange(OR) %>%
# mutate(pos2 = row_number()) %>%
# select(Variable, pos) %>%
# inner_join(data) %>%

plot_ly(
  fig,
  x = ~pos,
  y = ~`max_OR-inv_OR`,
  size = ~-log10(p),
  color = ~theme,
  frame = ~week,
  text = ~Variable,
  alpha = 0.75,
  symbol = ~shape,
  symbols = c(219, 220),
  hooverinfo = "text",
  type = "scatter",
  mode = "markers"
  # error_y = list(array = ~inf,
  #                arrayminus = ~sup,
  #                symmetric = FALSE,
  #                type = "data")
) %>%
  layout(
    xaxis = list(title = "Variable"),
    yaxis = list(title = "max(OR, 1/OR)"))

@@

<!-- === -->
```{r, eval = F, echo = F}
vacc_com = read_csv2(url(paste0("https://datavaccin-covid.ameli.fr/explore/dataset/donnees-de-vaccination-par-commune/download/?format=csv&refine.classe_age=", "TOUT_AGE", "&refine.semaine_injection=2021-", "27", "&timezone=Europe/Berlin&lang=fr&use_labels_for_header=true&csv_separator=%3B"))) %>%
  mutate(codgeo = as.numeric(commune_residence)) %>%
  mutate(taux_cumu_1_inj = as.numeric(taux_cumu_1_inj))

vacc = read_csv2(url(paste0("https://datavaccin-covid.ameli.fr/explore/dataset/donnees-de-vaccination-par-epci/download/?format=csv&refine.semaine_injection=2021-", "27", "&refine.classe_age=", "TOUT_AGE", "&timezone=Europe/Berlin&lang=fr&use_labels_for_header=true&csv_separator=%3B"))) %>%
  mutate(codgeo = as.numeric(epci)) %>%
  mutate(taux_cumu_1_inj = as.numeric(taux_cumu_1_inj)) %>%
  plyr::rbind.fill(vacc_com)

@@

(t=table(test$Overcrowding_rate, test$taux_cumu_1_inj))

questionr::odds.ratio(factor(test$Overcrowding_rate, levels = c(0,1), labels = c(0,1)), test$taux_cumu_1_inj)
epitools::oddsratio(x = t, method = "fisher")
```

@@

fig = data %>%
  mutate(shape = if_else(OR > 1, 219, 220)) %>%
  mutate(inf = if_else(OR > 1, `2.5 %`, `inv_2.5 %`),
         sup = if_else(OR > 1, `97.5 %`, `inv_97.5 %`),
         value = (sup-inf))
# filter(week == 33) %>%
# arrange(OR) %>%
# mutate(pos2 = row_number()) %>%
# select(Variable, pos) %>%
# inner_join(data) %>%

plot_ly(
  fig,
  x = ~pos,
  y = ~`max_OR-inv_OR`,
  size = ~-log10(p),
  color = ~theme,
  frame = ~week,
  text = ~Variable,
  alpha = 0.75,
  symbol = ~shape,
  symbols = c(219, 220),
  hooverinfo = "text",
  type = "scatter",
  mode = "markers"
  # error_y = list(array = ~inf,
  #                arrayminus = ~sup,
  #                symmetric = FALSE,
  #                type = "data")
) %>%
  layout(
    xaxis = list(title = "Variable"),
    yaxis = list(title = "max(OR, 1/OR)"))

@@

<!-- # Données de vaccination nationales -->

```{r, echo = F, warning = F, message = F, eval = F}
wk = 37

vacc_com = read_csv2(url(paste0("https://datavaccin-covid.ameli.fr/explore/dataset/donnees-de-vaccination-par-commune/download/?format=csv&refine.semaine_injection=2021-", wk, "&timezone=Europe/Berlin&lang=fr&use_labels_for_header=true&csv_separator=%3B"))) %>%
  mutate(codgeo = as.numeric(commune_residence)) %>%
  mutate(week = wk) %>%
  select(codgeo, classe_age, population_carto, effectif_cumu_1_inj, week)

vacc %>%
  filter(!is.na(effectif_cumu_1_inj)) %>%
  group_by(classe_age) %>%
  summarise(pop = sum(population_carto, na.rm = T),
            tot_vacc = sum(effectif_cumu_1_inj, na.rm = T)) %>%
  ungroup() %>%
  mutate(tx_vacc = tot_vacc/pop)
```
